Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-21 Grassmannian_cells.tex
Major reorganization - part 2

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
\usepackage{pgflibraryarrows}
\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\usepackage{verbatim}
\input xy
\xyoption{all}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Torus Actions on Quiver Grassmannians}
\label{torusaction}

\subsection{Bialynicki-Birula decomposition}
The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general. If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula. More detailed, let $X$ be a smooth projective variety with a $\C^\ast$-action. For a connecting component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[\mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}\]

Then we have the following statement, \cite[Section 4]{bb}:
\begin{theorem}Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components. Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$ where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$. Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and
the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.

In particular, we have $\chi(X)=\chi(X^{\C^\ast})$ for the Euler characteristic.
\end{theorem}

\noindent 
Fix a vector space $X$ of dimension $n$ and let $d\leq n$. We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$. Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner. Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$. We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e. there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$. Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$. This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$. We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e. there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
where the unit vectors are in the columns $i_1,\ldots,i_d$. All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$. The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e. we have
\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
\begin{lemma}\label{usualGrass}
Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
\end{lemma}
\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
where $j_0=0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
\begin{itemize}
  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
\end{itemize}

@@

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}
  \footnote{This needs to be cleaned up, the proof seems false as written.}
  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
\end{proof}

In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.
Following Lemma~\ref{le:injective evaluation maps} we define the following.
\begin{definition}
  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

@@

\subsection{Understanding Truncated Preprojectives}

@@

\subsection{Results on the universal cover $\widetilde{K(n)}$}

@@

\begin{align*}\xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.

The representation $\tilde P_3$ is given by the quiver
	\begin{align*}\xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}\end{align*}
	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.  Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.  The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
	\begin{align*}\xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}\end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.

@@

\subsection{Action on arrows}
Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
\begin{proposition}\label{indecomposables}Let $m\geq 1$. Let $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$. Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$. The following holds:
\begin{enumerate}
\item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
\item The set indecomposable representations of dimension $\alpha(m,r)$ ist given by a non-empty open subset of $R_\alpha(K(n))$. 
\item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
\end{enumerate}
\end{proposition}
\begin{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial description of non-empty cells}
In this section we provide a direct quiver theoretic description of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
The key concept is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations, though it will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
\begin{definition}
  Let $Q=(Q_0,Q_1)$ be a quiver.
  A subset $\beta\subset Q_0$ is \emph{successor closed} if for each $p\in\beta$, the existence of an arrow $v:p\to q$ in $Q_1$ implies $q\in\beta$.

@@

This defines recursively the representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ when considering the short exact sequences
\[\ses{P_1}{P_2^{(k)}}{P_2^{(k+1)}}\]
by the coefficient quivers
\begin{align}\label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.\end{align}
Note that we have a short exact sequence
\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
We define the $2$-quiver of $P_2^{(k)}$ by
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compatible Pairs Label Cells in $Gr^Q_\bfe(P_m)$}
For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.

>>>>

\documentclass{amsart}

% Commands for marginal notes
\usepackage[draft]{say}
\newcommand{\sayD}[1]{\say[D]{#1}}
\newcommand{\sayT}[1]{\say[T]{#1}}

\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
\usepackage{pgflibraryarrows}
\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in,marginparwidth=0.8in, marginparsep=0.1in]{geometry}
\usepackage{extarrows}
\usepackage{verbatim}
\input xy
\xyoption{all}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}

Fix $n\ge3$. Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
The category $\rep K(n)$ of finite-dimensional representations of $K(n)$ is equivalent to the category of modules over the path algebra $A(n)$ of $K(n)$.
As a $\CC$-vector space, the path algebra $A(n)$ can be written as $A_0\oplus A_1$, where 
\begin{itemize}
  \item $A_0=\CC e_1\oplus \CC e_2$ is a two-dimensional semisimple algebra with orthogonal idempotents $e_1$ and $e_2$;
  \item $A_1=\bigoplus_{i=1}^n \CC a_i$ is the $A_0$-bimodule spanned by the arrows of $K(n)$, that is $e_ka_ie_\ell=\delta_{k1}\delta_{\ell2}a_i$ for $1\le i\le n$ and $k,\ell\in\{1,2\}$.
\end{itemize}

@@

\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}
%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
\begin{proof}
  \footnote{This needs to be cleaned up, the proof seems false as written.}
  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
\end{proof}
In what follows we will not distinguish between $P_m\otimes V$ and its image under $ev_V$.

\subsection{Truncated Preprojectives}
\label{sec:truncated preprojectives}
Following Lemma~\ref{le:injective evaluation maps} we define the following.
\begin{definition}
  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

@@

@@

\subsection{Lifting to $\widetilde{K(n)}$}

@@

\begin{align*}
  \xymatrix@R10pt@C20pt{&&(1,a_1)\\(2,1)\ar^{a_1}[rru]\ar^{a_{n}}[rrd] &&\vdots\\&&(1,a_n)}
\end{align*}
The support of $\tilde P_2^{(i)}$, which we denote by $\mathcal A_i$ during this proof, can be obtained from this quiver by erasing the arrow $a_i$ and the corresponding sink. In turn, the quiver of $\tilde P_2^{(j_1,\ldots,j_l)}$ is obtained by erasing the arrows $a_{j_1},\ldots, a_{j_l}$.

The representation $\tilde P_3$ is given by the quiver
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&\mathcal A_1\ar_{a_{1}}[lld]\\ n-1 &&\vdots\\&&\mathcal A_n\ar_{a_{n}}[llu]}
        \end{align*}
	where the vertex of dimension $n-1$ is the middle vertex $(2,1)$.  Moreover, for $\uj\in I_l$, the representation $\tilde P_3^{\uj}$ is obtained when erasing the subquivers $\mathcal A_{j_1},\ldots,\mathcal A_{j_l}$ and decreasing the dimension of $(2,1)$ by one.  The Auslander-Reiten translate $\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ is given by
	\begin{align*}
          \xymatrix@R10pt@C20pt{&&(2,a_{j_1}^{-1})\ar_{a_{j_1}}[lld]\\(1,1) &&\vdots\\&&(2,a_{j_l}^{-1})\ar_{a_{j_l}}[llu]}
        \end{align*}
In particular, the image of the unique homomorphism $\tilde P_{2,j_i}=a^{-1}_{j_i}.\tilde P_2\to\tau\tilde P_{3}^{(j_1,\ldots,j_l)}$ has image $(2,a_{j_i}^{-1})\xrightarrow{a_{j_i}}(1,1)$ for $i=1,\ldots,l$.

@@

\subsection{Bialynicki-Birula decomposition}
The aim of Section \ref{torusaction} is to define a torus action on quiver Grassmannians which can be used to simplify the calculation of homological invariants in general.
If the quiver Grassmannian is smooth, which is for instance the case for exceptional representations by \cite{cr}, it can also be used to stratify the quiver Grassmannians using the results of Bialynicki-Birula.
More specifically, let $X$ be a smooth projective variety with a $\C^\ast$-action.
For a connected component of the fixed point set $C\subset X^{\C^\ast}$, we define its attracting set as
\[
  \mathrm{Att}(C):=\{y\in X\mid \lim_{t\to 0}t.y\in C\}
\]

The following result of Bialynicki-Birula relates the geometry of $X$ to the geometry of its torus fixed points.
\begin{theorem}
  \cite[Section 4]{bb}
  Let $\coprod_{i=1}^r C_i= X^{\C^\ast}$ be the decomposition into connected components.
  Then $\mathrm{Att}(C_i)$ is a locally closed smooth $\C^\ast$-invariant subvariety of $X$, where $C_i$ is a subvariety of $\mathrm{Att}(C_i)$.
  Moreover, we have $X=\coprod_{i=1}^r\mathrm{Att}(C_i)$ and the natural map $\gamma_i:\mathrm{Att}(C_i)\to C_i$ is an affine vector bundle.

  In particular, we have an equality of Euler characteristics $\chi(X)=\chi(X^{\C^\ast})$.
\end{theorem}

\subsection{Torus Actions}
\label{torusaction}

Fix a vector space $X$ of dimension $n$ and let $d\leq n$. We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$. Then we generalize the concept to quiver Grassmannians, but we will see that the torus fixed point set can be calculated in an analogous manner. Thus assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$. We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of $X$ which is compatible with this decomposition, i.e. there exist numbers $1\leq j_1\leq j_2\ldots\leq j_{l-1}\leq n$ such that
\[v_1,\ldots,v_{j_1}\in X_1,\,v_{j_1+1},\ldots,v_{j_2}\in X_2,\ldots,v_{j_{l-1}+1},\ldots,v_{n}\in X_l\]
Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$. Then there exists a $\C^\ast$-action on $X$ when extending the definition $t.v_i:=t^{d(j)}v_i$ if $v_i\in X_j$ linearly to $X$. This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_d(X)$. We can write every $U\in\Gr_d(X)$ uniquely in row-echelon form with respect to the basis $\mathcal B$, i.e. there exists a unique sequence $1\leq i_1\leq\ldots\leq i_d\leq n$ and a unique matrix representation of $U$ of the form
\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{d,n}(k)\]
where the unit vectors are in the columns $i_1,\ldots,i_d$. All matrix representations of this form define a Schubert cell $X_{\bfi}$ where $\bfi=(i_1,\ldots,i_d)$. The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e. we have
\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}.\]
Every Schubert cell is invariant under the torus action, i.e. $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
\begin{lemma}\label{usualGrass}
Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$, $v_{i'}\in X_{j'}$ and $j\neq j'$.
Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
\end{lemma}
\begin{proof}If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_i+1)}(U\cap X_i)=U\]
where $j_0=0$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$GL_n$ Action on Arrows of $K(n)$}
Observe that $GL_n(\CC)$ naturally acts on $A_1$ and hence $GL_n(\CC)$ acts on $\rep K(n)$ via the induced action on $A(n)$.
More precisely, given a representation $M=(M_1,M_2,M_{a_i})$ of $K(n)$ and $g=(g_{ij})\in GL_n(\CC)$, the representation $g.M$ is given by $(M_1,M_2,M'_{a_i})$ with $M'_{a_i}=\sum\limits_{j=1}^n g_{ij}M_{a_j}$.
Note that $M$ and $g.M$ are not necessarily isomorphic as representations of $K(n)$.
\begin{lemma}
  \label{le:hom equivariance}
  For any morphism $\theta:M\to N$ between representations $M,N\in\rep K(n)$, the same maps $\theta_1:M_1\to N_1$ and $\theta_2:M_2\to N_2$ give a morphism $\theta^g:g.M\to g.N$ for any $g\in GL_n(\CC)$.
  In particular, the hom-spaces $\Hom(M,N)$ and $\Hom(g.M,g.N)$ are canonically identified for each $g\in G$.
\end{lemma}
\begin{proof}
  Suppose $\theta:M\to N$ is a morphism of representations, i.e.\ $\theta_2\circ M_{a_j}=N_{a_j}\circ\theta_1$ for $1\le j\le n$.
  Then for $g=(g_{ij})\in GL_n(\CC)$, we have
  \[\theta_2\circ M'_{a_i}=\sum\limits_{j=1}^n g_{ij}(\theta_2\circ M_{a_j})=\sum\limits_{j=1}^n g_{ij}(M_{a_j}\circ\theta_1)=N'_{a_i}\circ\theta_1\]
  for $1\le i\le n$ so that $\theta$ also gives a morphism from $g.M$ to $g.N$. 
\end{proof}
\begin{corollary}
  \label{cor:indecomposability}
  For $M\in\rep K(n)$ and $g\in GL_n(\CC)$, the representation $M$ is indecomposable if and only if $g.M$ is indecomposable.
\end{corollary}
\begin{proof}
  The representation $M$ is decomposable if there exists a split epimorphism $\theta:M\onto N$ for some nonzero representation $N$.
  But this occurs exactly when the map $\theta^g:g.M\onto g.N$ is also a split epimorphism.
\end{proof}

@@

%Any subrepresentation $E\subset P_{m+1}^V$ corresponds by taking pullbacks to a chain of inclusions $P_m\otimes V\subset\tilde E\subset P_{m+1}$.
\begin{proposition}
  \label{indecomposables}
  Let $m\geq 1$.
  Let $\alpha(m,r)=\dim P_{m+1}-r\dim P_m$ with $0\leq r\leq n-1$.
  Let $R_\alpha(K(n))$ be the affine space of representations of dimension $\alpha(m,r)$.
  The following hold:
  \sayD{Move the first two of these into section~\ref{sec:truncated preprojectives}?}
  \begin{enumerate}
    \item The isomorphism classes of indecomposable representations of dimension $\alpha(m,r)$ are in one-to-one correspondence to points of $\Gr_{n-r}(\CC^n)$.
    \item The set indecomposable representations of dimension $\alpha(m,r)$ is given by a non-empty open subset of $R_\alpha(K(n))$. 
    \item The action of $\Gl_n(\CC)$ is transitive on $\mathrm{Ind}(K(n),\alpha(m,r))$.
  \end{enumerate}
\end{proposition}
\begin{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Combinatorial description of non-empty cells}
In this section, we provide two combinatorial descriptions of the non-empty cells in the quiver Grassmannians of (truncated) preprojective representations of $K(n)$.
The first is quiver theoretic and follows directly from the recursive construction of the cell decomposition.
The second is the notion of compatible pairs in a maximal Dyck path.
We give a bijection between these which provides a partial answer to a question of the first author.

\subsection{$2$-Quivers}

The key concept for describing the cell decompositions is the following notion of $2$-quiver which is closely related to certain coefficient quivers of the corresponding representations, though it will turn out that a feature of this construction is that it is blind to the coloring of the different arrows of $\widetilde K(n)$ covering the arrows of $K(n)$.
\begin{definition}
  Let $Q=(Q_0,Q_1)$ be a quiver.
  A subset $\beta\subset Q_0$ is \emph{successor closed} if for each $p\in\beta$, the existence of an arrow $v:p\to q$ in $Q_1$ implies $q\in\beta$.

@@

This defines recursively the representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ when considering the short exact sequences
\[\ses{P_1}{P_2^{(k)}}{P_2^{(k+1)}}\]
by the coefficient quivers
\begin{align}
  \label{coeff}\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.
\end{align}
Note that we have a short exact sequence
\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
We define the $2$-quiver of $P_2^{(k)}$ by
\\

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compatible Pairs}
For $m\ge1$, let $D_m$ denote the maximal Dyck path in the lattice rectangle with corner vertices $(0,0)$ and $(u_m,u_{m-1})$.  
More precisely, $D_m$ is the lattice path which begins at $(0,0)$, takes East and North steps to end at $(u_m,u_{m-1})$, and never passes above the main diagonal joining $(0,0)$ and $(u_m,u_{m-1})$.  
It is maximal in the sense that any lattice point lying strictly above $D_m$ also lies above the main diagonal.
